Relationships in the extremes and their influence on competition and coexistence

### 2022-03-04 paper/Paper.Rnw
adding to discussion

We note that our expansion, like the decomposition of \cite{Ellner_2019} is generalizable to multi-species and multi-driver models. Because asymmetric tail associations exist in many ecological variables \citep{Ghosh_2020_AER}, the more specified approach of considering unique drivers of coexistence rather than E and C and the ability to consider more than two drivers, could produce interesting results??

@@

%Also need to talk about how this stuff will apply to data.
As an introductory investigation of ATAs within the framework of coexistence theory, 
we used simple and extreme examples, and future work should include more realism and complexity
(assess more complex relationships, systems, and models). 
In our theoretical exploration, we implemented a simple lottery model and assessed 
the influence of extremely asymmetric associated noise, i.e., the noise was perfectly correlated
in exactly one half of the distribution. However, more complex models such as structured demographic models
or integral projection models should be explored and though similar results may be
produced, varying deegres of ATA, less extremely shaped?/
more moderately asymmetric / more realistic? relationships should be implemented.
Moreover, because our empirical application makes use of a simple and controlled lab system, future 
should be done to assess the extent of how much ATA are important for complex systems and field systems.

>>>>

We note that our expansion, like the decomposition of \cite{Ellner_2019} is generalizable to multi-species and multi-driver models. Because asymmetric tail associations exist in many ecological variables \citep{Ghosh_2020_AER}, the more specified approach of considering unique drivers of coexistence rather than E and C and the ability to consider more than two drivers, could produce interesting results?? 
More species and more drivers= more things that can be related

@@

%Also need to talk about how this stuff will apply to data.
As an introductory investigation of ATAs within the framework of coexistence theory, 
we used simple and extreme examples, and future work should include more realism and complexity
(assess more complex relationships, systems, and models). 
In our theoretical exploration, we implemented a simple lottery model and assessed 
the influence of extremely asymmetric associated noise, i.e., the noise was perfectly correlated
in exactly one half of the distribution. However, more complex models such as structured demographic models
or integral projection models should be explored and though similar results may be
produced, varying deegres of ATA, less extremely shaped?/
more moderately asymmetric / more realistic? relationships should be implemented.
Moreover, because our empirical application makes use of a simple and controlled lab system, future 
should be done to assess the extent of how much ATA are important for complex systems and field systems.
For example, the ATAs between rainfall timing on the coexistence of grasses and forbs 
and their dominant years in California grasslands \citep{Hallett_2019} could be a fruitful 
further investigation of biodiversity maintenance in California grasslands and the effects of extreme rainfall fluctuation.
